Comparison of Associative Data Structures

### 2014-04-09 final_presentation/presentation.tex
Last minor changes.

\begin{frame}{Small hash tables are expensive}
    \centering
    \includegraphics[width=0.8\textwidth]{hashtable_bad.png}
\end{frame}

\begin{frame}{Big hash tables are cheap}
    \centering
    \includegraphics[width=0.8\textwidth]{hashtable_good.png}
\end{frame}

@@

\begin{frame}{Number of entries}
    \begin{figure}
      \centering
        \includegraphics[width=0.95\textwidth]{SkiplistMemory}
      \caption{The average duration of each query operation, plotted against the total number of entries.}
    \end{figure}
\end{frame}

\begin{frame}{Binary search tree}
    \begin{itemize}
        \item For IP adresses: Significantly faster insertions than both other structures for low number of entries.
        \item Scales badly compared to the other structures.
        \item Other keys: Always slower than a hash table.
    \end{itemize}
\end{frame}

>>>>

\begin{frame}{Small hash tables are expensive}
    \centering
    \includegraphics[width=\textwidth]{hashtable_bad.png}
\end{frame}

\begin{frame}{Big hash tables are cheap}
    \centering
    \includegraphics[width=\textwidth]{hashtable_good.png}
\end{frame}

@@

\begin{frame}{Number of entries}
    \begin{figure}
      \centering
        \includegraphics[width=0.82\textwidth]{SkiplistMemory}
      \caption{The average memory usage per entry, plotted against the total number of entries.}
    \end{figure}
\end{frame}

\begin{frame}{Binary search tree}
    \begin{itemize}
        \item For IP adresses: Significantly faster insertions than both other structures for low numbers of entries.
        \item Scales badly compared to the other structures.
        \item Other keys: Always slower than a hash table.
    \end{itemize}
\end{frame}
